### 2014-03-07 docs/related-work.tex
Add how GFW blocks Tor.

Traffic using covert channels may exhibit distinguishable characteristics. As
noted by Winter et al.~\cite{foci12-winter}, Tor traffic is currently
distinguishable from what is regarded as harmless traffic. Therefore, another
school of research focuses on obfuscation techniques for hiding protocol
patterns. One technique is to look unlike anything forbidden by the censor; that
is, fail to match a blacklist. Another is to resemble a protocol that is
explicitly allowed; that is, match a whitelist. Falling into the first category
are ``look-like-nothing'' transports whose payloads are indistinguishable from a
uniformly random byte stream. A examples of such a transport is
obfsproxy~\cite{obfsproxy}, long the go-to obfuscated transport used by Tor.
ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the content of its
payloads, but takes additional steps to obscure its signature of packet lengths
and timing, and is designed to resist active scanning for proxies (the proxy
server says nothing until the client proves knowledge of a shared secret).
Another path to obfsucation is the steganographic approach: look like something
the censor doesn't block. StegoTorus~\cite{stegotorus} and Code Talker Tunnel
(formerly called SkypeMorph)~\cite{skypemorph} camouflage Tor traffic and
attempt to mimic HTTP or Skype traffic. CensorSpoofer also mimics SIP-based VoIP
to hide the upstream channel.\\

@@

How the GFW is blocking Tor. \cite{foci12-winter}\\

GoAgent~\cite{goagent} is a direct inspiration for our work in its use of App
Engine and Host header--based domain fronting. GoAgent requires users to upload
a personal copy of the server code to App Engine, and App Engine itself makes
HTTP requests, not some proxy farther out. According to a May 2013 survey~\cite
{collateral-freedom}, GoAgent was then the circumvention tool most used in
China, with 35\% of survey respondants having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
\\

>>>>

Traffic using covert channels may exhibit distinguishable characteristics. As
noted by Winter et al.~\cite{foci12-winter}, Tor traffic is currently
distinguishable from what is regarded as harmless traffic. In addition, their
experiments show that the Great Firewall of China actively scans for Tor bridges
and block them. Therefore, another school of research focuses on obfuscation
techniques for hiding protocol patterns. One technique is to look unlike
anything forbidden by the censor; that is, fail to match a blacklist. Another is
to resemble a protocol that is explicitly allowed; that is, match a whitelist.
Falling into the first category are ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream. A examples
of such a transport is obfsproxy~\cite{obfsproxy}, long the go-to obfuscated
transport used by Tor. ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the
content of its payloads, but takes additional steps to obscure its signature of
packet lengths and timing, and is designed to resist active scanning for proxies
(the proxy server says nothing until the client proves knowledge of a shared
secret). Another path to obfsucation is the steganographic approach: look like
something the censor doesn't block. StegoTorus~\cite{stegotorus} and Code Talker
Tunnel (formerly called SkypeMorph)~\cite{skypemorph} camouflage Tor traffic and
attempt to mimic HTTP or Skype traffic. CensorSpoofer also mimics SIP-based VoIP
to hide the upstream channel.\\

@@

GoAgent~\cite{goagent} is a direct inspiration for our work in its use of App
Engine and Host header--based domain fronting. GoAgent requires users to upload
a personal copy of the server code to App Engine, and App Engine itself makes
HTTP requests, not some proxy farther out. According to a May 2013 survey~\cite
{collateral-freedom},  GoAgent was then the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
\\
